{\small Topic 21: AUG experiment analsysis meeting }

### 2017-09-15 Meetings/AUGrelated/interim_meeting_150917.tex
Update to the presentation of 15-09-17

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: AUG experiment analsysis meeting }}
\date{15 September 2017}
\author[Topic 21 Scientific Team]{N. Vianello and V. Naulin for the
  Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Summary of the campaigns}
  \begin{itemize}[<+-|alert@+>]
  \item L-Mode experiment, CW 17.
    \begin{enumerate}
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
    \end{enumerate}    
    \item H-Mode experiment, CW 21. 
      \begin{enumerate}
    \item<2> Compare divertor/midplane fueling effect on filamentary
      transport and profiles without cryo-pumps
    \item<2> Compare profiles with the same fueling with/without cryopums
    \item<2> Determine an H-Mode with the cryopumps matching similar
      divertor pressure and SOL profiles
    \end{enumerate}
  \end{itemize}    
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3-> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<4-> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_t$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<3-> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<4-> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

% \begin{frame}{Compare Similar fueling with/without cryopumps}
% \Fontvi
%   \vspace{-1cm}
% \begin{columns}
%   \begin{column}{0.65\textwidth}
%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
%   \end{column}
%   \begin{column}{0.35\textwidth}
%     \begin{itemize}
%       \item<1-> Same fueling but with cryo-pumps. Clearly different in
%         terms of Edge density and Divertor pressure
%       \item<2-> Also with this amount of fueling any instance of SOL
%         saturation observed
%     \end{itemize}

%   \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}{Matching scenarios with cryo-pumps}
% \Fontvi
%   \vspace{-1cm}
% \begin{columns}
%   \begin{column}{0.65\textwidth}
%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34280}}
%   \end{column}
%   \begin{column}{0.35\textwidth}
%     \begin{itemize}
%       \item<1-> To match similar edge density and divertor pressure
%         and to reach the same level of detachment we increase the
%         fueling by almost a factor of 3, increasing also the rate. In
%         addition to that we also increase substantially the N puffing
%       \item<2-> Li-beam profile not yet produced for the same
%         shots. With a lower level of N (no detachment observed) the
%         SOL profiles does not flatten as in the case with the cryo-pumps
%     \end{itemize}
%   \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}{Work in progress}
%   \begin{itemize}
%     \item Confirmed SXR spikes correlated with the start of ELMs,
%       strongly suggesting electron accelleration during ELM filament
%       eruption
%     \item Evaluation progressing in terms of fluctuation analysis from
%       MEM, Reflectometry, Li-Beam
%     \item GPI data available in different density scenarios and also
%       during L-H transition
%   \end{itemize}
% \end{frame}
\end{document}

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: AUG experiment analsysis meeting }}
\date{15 September 2017}
\author[N. Vianello]{N. Vianello and V. Naulin for the
  Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Summary of the campaigns}
  \begin{itemize}[<+-|alert@+>]
  \item L-Mode experiment, CW 17.
    \begin{enumerate}
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
      \item<1-> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
    \end{enumerate}    
    \item H-Mode experiment, CW 21. 
      \begin{enumerate}
    \item<2> Compare divertor/midplane fueling effect on filamentary
      transport and profiles without cryo-pumps
    \item<2> Compare profiles with the same fueling with/without cryopums
    \item<2> Determine an H-Mode with the cryopumps matching similar
      divertor pressure and SOL profiles
    \end{enumerate}
  \end{itemize}    
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
        $\Lambda_{div}$ without sensible difference among the current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_t$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantBt}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<3|only@3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \item<3|only@3> Still need to provide detail evolution of edge
        profiles as a function
        of $\Lambda_{div}$ which are different at different current
        although same L$_{\parallel}$
      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
        different current even though obtained at different values of $\Lambda_{div}$. 
      \item<4|only@4> Remarkable difference in the shape of typical
        structure,  even though $\tau_{ac}$ follow usual trend apart
        from very last points. \alert{To be double-checked}
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{H-Mode investigation: puffing location}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item Similar puff from Lower and Upper divertor valves
        (\alert{we asked for divertor/midplane valves})
      \item<2-> Edge density profiles from Li-Beam evolution are
        pretty similar
      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
        for the available shot
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Compare Similar fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> Same fueling but with cryo-pumps. Clearly different in
        terms of Edge density and Divertor pressure
      \item<2-> Also with this amount of fueling no instance of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<3> Comparison of fluctuations during the plunge at higher
        density (\alert{ELM included}) reveal differences in
        fluctuations. \alert{ELM resolved measurement to be properly done}

    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    %\centering{\includegraphics<3>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N puffing
      \item<2-> Without cryopumps evidence of stronger SOL profile
        flattening from Li-Be. \alert{To be compared with appropriate
          variation of $\Lambda_{div}$}
      % \item<3> Clear difference in the shape of I$_s$ structure and in
      %   PDF although it is not yet \alert{ELM resolved}
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{What is missing}
  \Fontvi
  \begin{enumerate}
    \item RIC profiles with possible poloidal variation among the
      antennas in particular in H-Mode. \textcolor{red}{To be done}
    \item Li-Be ELM resolved profile variation with $\Lambda_{div}$
      \textcolor{red}{To be done}
    \item Li-Be fluctuations \textcolor{red}{To be done}
    \item Structures size and velocities in L-Mode
      \textcolor{orange}{In progress}
    \item Radiation front movement \textcolor{orange}{In progress}
    \item Can we have from stark-broadening the movement of density
      front towards the X-Point \textcolor{red}{To be done, maybe not
        feasible}
    \item Neutrals analysis from D$_{\alpha}$ camera
      \textcolor{orange}{In progress}
    \item Fast-camera \textcolor{red}{To be done}
    \item Other?
  \end{enumerate}
\end{frame}

\begin{frame}{2018}
  \textbf{Just a brainstorming exercise so far}
  \begin{itemize}
    \item X-point probe. Realistically there should be man-power for
      proper operation and we need information below the midplane
      before entering the divertor region
    \item NPH evaluation of Ti
    \item Parallel and perpendicular momentum variation at high
      density. We already know there is a change in the perpendicular
      flow to be complemented with parallel flow as well
    \item Divertor modification? I guess SP movement is not feasible
      in AUG but keeping the SP at the same position and moving the
      X-point (vertically/radially) can induce some modification?
    \item Increasing the density through pellet is feasible?
    \item Isotope effect? In case campaign is foreseen we could change
      parallel flow and recycling (?)
  \end{itemize}
\end{frame}
\end{document}
